\thetitle

### 2013-04-18 tfpie/tfpie.tex
start on more transitions
sec 5.2

\cite{dvanhorn:Ragde2008Chilling}
\cite{dvanhorn:Chakravarty2004Risks}

>>>>

Of course, not every curriculum that begins with \htdp transitions to
Java after the first course.  \citet{dvanhorn:Ragde2008Chilling}
describes a second course that includes both more advanced work in
Scheme beyond teaching-oriented languages as well as low-level
programming in C, taught to computer science majors at University of
Waterloo.  Radge's course intentionally does not use student-oriented
languages, although the recently-developed C0 language~\cite{local:c0}
could provide this. Other discussions of functional programming in the
first year~\cite{dvanhorn:Chakravarty2004Risks} do not discuss the
problems of transition.
